---
title: "My Quarto Document"
author: "Lance Lowell"
date: "2025-03-01"
format: html
execute:
  echo: true
---
#Use the help (?) function to learn more about the dataset
```{r}
library(tidyverse)
library(visdat)
library(broom)

data("airquality")

?airquality
```
 
#Use vis_dat to check out the data
```{r}
vis_dat(airquality)
vis_miss(airquality)
```
#It clearly needs cleaning as 4.8% of the data is missing!

#Fit a linear model to the cleaned data to predict Ozone from one of the possible predictors of your choosing. Why did you chose that variable?
```{r}
airquality_clean <- airquality %>% drop_na()

model <- lm(Ozone ~ Temp, data = airquality_clean)
```
#I chose temperature because I want to see the relationship between Ozone and temperature like my prfessors have talked about in my other ESS couses for myself.



#Using summary(), Does this seem like a valid model?
```{r}

summary(model)
```
#This is not a valid model.
#The R squared value says only 48.8%  (48.3% adjusted) of the variability in ozone levels can be explained by changes in temperature.  That means less than half of the data is explained by the model

#Use broom::augment to predict the Ozone of the cleaned data
```{r}
predictionstation <- broom::augment(model, airquality_clean)

head(predictionstation)
```

#Use ggplot to plot the actual vs predicted Ozone
```{r}
ggplot(predictionstation, aes(x = Ozone, y = .fitted)) +
  geom_point(color = "navy") +  
  ##Add a red line to show where the actual and predicted values are equal
  geom_abline(intercept = 0, slope = 1, color = "red") +
#Add a subtitle to the plot showing the correlation between the actual and predicted values are equal
  labs(
    title = "Actual vs Predicted Ozone",
    subtitle = paste("Correlation:"),
    x = "Real Ozone",
    y = "Predicted Ozone"
  ) +
  theme_classic()
```


